Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-07 PaperVictor.tex
Revise abstract

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance $\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors  averaged over a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We found \notaL{No
  estoy seguro del tiempo} that
chirped structures were better suited for the Vis stacked
sub-mirrors for the NIR region. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} have
reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective
oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has
increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce photonic mirrors
that have a large reflectance over a wide band-width with a relatively
small thickness and refractive index contrast. Specifically, our aim
is to maximize the reflectance $R$ averaged over a wide range of
wavelengths $\lambda$ and angles of incidence $\theta$.

@@

\notaL{Pon etiquetas a todo para poderlo referir}
For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method\notaL{reference}. Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
  sería de 4x4}, the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
  explicarlas, y no creo que sean importantes para el lector} are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
  estaban en la fórmula} The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que esto debería estar más adelante:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}

>>>>

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the average \notaV{Agregue} reflectance $\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors within \notaV{Agregue y quite "averaged over"} a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We find \notaL{No
  estoy seguro del tiempo} that
chirped structures are more suitable for the Vis range, while stacked
sub-mirrors are better for the NIR region. \notaV{Corregi oracion} We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} \notaV{Comentario atendido} have
reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al. \cite{Park2003},
used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective
oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has
increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce photonic mirrors
that have a large reflectance over a wide band-width with a relatively
small thickness and refractive index contrast. Specifically, our aim
is to maximize the reflectance $R$ averaged over a wide range of
wavelengths $\lambda$ and angles of incidence $\theta$.

@@

\notaL{Pon etiquetas a todo para poderlo referir}
For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
  sería de 4x4}, the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que esto debería estar más adelante:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
} \notaV{De acuerdo}
